### 2017-12-31 icde/revision/sec-incAlg.tex

%%% affected/unaffected division
\vspace{-1ex}
\stitle{Analysis of affected and unaffected areas}.
The TWPageRank vector $PR$ of graph $G$ is mainly affected in two ways.

@@

\stitle{Time complexity analysis of the incremental algorithm}.
By the analyses above, the time complexity of \incensemble is the same as \batensemble, except that \incensemble saves $O(|E^c_A\cup E^c_{AB}|)$ and $O(|E^v_A\cup E^v_{AB}|)$ time when computing TWPageRank  on the updated citation and venue graphs at an extra space cost for the affected/unaffected division and the copy of original edge weights.

Despite of its similar time complexity to \batensemble, algorithm \incensemble typically achieves a substantial efficiency improvement over \batensemble, according to our statistics of affected/unaffected areas given a yearly update, \ie articles of 2011 on \aan and 2015 on \aminer and \magdata, respectively, shown in Table~II.
%
(a) It saves $O(|V^c|+|E^c|)$ and $O(|V^v|+|E^v|)$ time when maintaining \sccs and the topological order based on the update data only,
%where ($|V^c|$, $|E^c|$, $|V^v|$, $|E^v|$) are more than (92\%, 89\%, 93\%, 89\%) of ($|V^{c,+}|$, $|E^{c,+}|$, $|V^{v,+}|$, $|E^{v,+}|$) on all tested graphs;
where ($|V|$, $|E|$) are more than (92\%, 89\%) of ($|V^{+}|$, $|E^{+}|$) on all tested citation and venue graphs;
(b) It saves $O(|E^c_A \cup E^c_{AB}|)$ time when updating scores on $V^c$, where edges in $E^c_A\cup E^c_{AB}$ account for more than 28\% of total;
(c) It saves $O(|E^c|)$ time when computing popularity of articles, which accounts for more than 89\% of total;
And, finally, (d) It is likely to compute TWPageRank scores on $V^c_B$ and $V^v_B$ with less iterations.

>>>>

%%% affected/unaffected division
\vspace{-.5ex}
\stitle{Analysis of affected and unaffected areas}.
The TWPageRank vector $PR$ of graph $G$ is mainly affected in two ways.

@@

\stitle{Time complexity analysis of the incremental algorithm}.
By the analyses above, the time complexity of \incensemble is the same as \batensemble, except that \incensemble saves $O(|E^c_A\cup E^c_{AB}|)$ and $O(|E^v_A\cup E^v_{AB}|)$ time when computing TWPageRank  on the updated citation and venue graphs with an extra space cost for the affected/unaffected division and the copy of original edge weights.

Despite of its similar time complexity to \batensemble, algorithm \incensemble typically achieves a substantial efficiency improvement over \batensemble, according to our statistics of affected/unaffected areas given a yearly update, \ie articles of 2011 on \aan and 2015 on \aminer and \magdata, respectively, shown in Table~II.
%
(a) It saves $O(|V^c|+|E^c|)$ and $O(|V^v|+|E^v|)$ time when maintaining \sccs and the topological order based on the update data only,
%where ($|V^c|$, $|E^c|$, $|V^v|$, $|E^v|$) are more than (92\%, 89\%, 93\%, 89\%) of ($|V^{c,+}|$, $|E^{c,+}|$, $|V^{v,+}|$, $|E^{v,+}|$) on all tested graphs;
where ($|V|$, $|E|$) are more than (92\%, 89\%) of ($|V^{+}|$, $|E^{+}|$) on all tested citation and venue graphs;
(b) It saves $O(|E^c_A \cup E^c_{AB}|)$ time when updating scores on $V^c$, where edges in $E^c_A\cup E^c_{AB}$ account for more than 28\% of total;
(c) It saves $O(|E^c|)$ time when computing popularity of articles, which accounts for more than 89\% of total;
Finally, (d) it is likely to compute TWPageRank scores on $V^c_B$ and $V^v_B$ with less iterations.

### 2017-12-31 icde/revision/sec-related.tex

PageRank \cite{Brin98:PageRank} and its extensions have been extensively used for citation analyses \cite{Waltman2014}. While PageRank equally propagates scores along outlinks, Weighted PageRank extends PageRank by distributing scores based on certain criteria such as popularity of pages~\cite{Xing04:WPR} or authority of authors~\cite{Ding11}.
%Both these approaches fail to capture the time-dependent characteristics, a key factor for scholarly article ranking.
Scholarly graphs belong to temporal graphs~\cite{temporalgraph}, and temporal information is a key factor for scholarly article ranking.
There has been work extending temporal information into PageRank, \eg exponentially decayed weights~\cite{Li08TSRanking}, exponentially decayed initial vectors~\cite{WalkerXKM07} and time-dependent weights based on co-authorship~\cite{FIALA2012370}.
%Different from previous work,
Differently, our Time-Weighted PageRank is designed based on a deep analysis of scholarly articles, and discriminately propagates scores in terms of citation statistics.

@@

Ensemble methods use multiple learners to obtain better performance than could be obtained from a constituent learner alone~\cite{zhihua-book}.
In this work, we leverage  importance assembling  to produce better and more robust results for scholarly article ranking~\cite{zhihua-book,wsdmcup,DuanAMHH16}.

>>>>

PageRank \cite{Brin98:PageRank} and its extensions have been extensively used for citation analyses \cite{Waltman2014}. While PageRank equally propagates scores along outlinks, Weighted PageRank extends PageRank by distributing scores based on certain criteria such as popularity of pages~\cite{Xing04:WPR} or authority of authors \cite{Ding11}.
%Both these approaches fail to capture the time-dependent characteristics, a key factor for scholarly article ranking.
Scholarly graphs belong to temporal graphs~\cite{temporalgraph}, and temporal information is a key factor for scholarly article ranking.
There has been work extending temporal information into PageRank, \eg exponentially decayed weights~\cite{Li08TSRanking}, exponentially decayed initial vectors~\cite{WalkerXKM07} and time-dependent weights based on co-authorship~\cite{FIALA2012370}.
%Different from previous work,
Differently, our Time-Weighted PageRank is designed based on a deep analysis of scholarly articles, and discriminately propagates scores in terms of citation statistics.

@@

Ensemble methods use multiple learners to obtain better performance than could be obtained from a constituent learner alone~\cite{zhihua-book}.
In this work, we leverage  importance assembling  to produce better and more robust ranking for scholarly articles~\cite{zhihua-book,wsdmcup,DuanAMHH16}.
